ABC inferences

### 2024-12-16 extensive_tests/abc_inferences/draft-abc-inferences-vignette.Rmd
Updating rule run_sim

>>>>

I got error with:

- `r-parallel`         # parallel for R

But it can be alternativelly installed by:

```{bash, eval = FALSE}
conda activate abc_inferences
R
install.packages("parallel")
## Another package it is still dependent on is
install.packages("devtools")
```

Then, the workflow can be run by:

```{bash, eval = FALSE}
conda activate abc_inferences
snakemake --use-conda
```
